Constraint Grammar as a SAT problem

### 2015-06-01 paper/nodalida2015.tex
yet more small fixes

Constraint Grammar (CG) \cite{karlsson1995constraint} is a relatively
young formalism. It belongs to the reductionist family of parsing
strategies, along with Finite-State Intersection Grammar (FSIG) \cite{koskenniemi90}.
In this work, we use a SAT solver to implement a version of CG that is
roughly compatible with CG-2.
This is attractive from several reasons: formal logic is
well-studied, and serves as an abstract language to reason about the
properties of CG. Constraint rules encoded in logic capture richer
dependencies between the tags than standard CG.

@@

Our work is inspired by \cite{lager98}, which presents constraint
rules as a disjunctive logic program, and \cite{lager_nivre01}, which
reconstructs four different formalisms in first-order logic.
\cite{lindberg_eineborg98ilp} and \cite{asfrent14} use Inductive Logic Programming to learn CG rules from a tagged corpus.
We explore different approaches to ordering. In the case of unordered
rules, it resembles Finite-State Intersection Grammar \cite{koskenniemi90}.
See also \cite{lager01transformation} for discussion of ordering of
the CG rules.

>>>>

Constraint Grammar (CG) \cite{karlsson1995constraint} is a relatively
young formalism, born out of empirical linguistic approach. 
It belongs to the reductionist family of parsing
strategies, along with e.g. Finite-State Intersection Grammar (FSIG) \cite{koskenniemi90}.
In this work, we implement CG\footnote{Roughly compatible with CG-2}
using a SAT solver. This is attractive from several reasons: formal logic is
well-studied, and serves as an abstract language to reason about the
properties of CG. Constraint rules encoded in logic capture richer
dependencies between the tags than standard CG.

@@

Our work is primarily inspired by \cite{lager98}, which presents constraint
rules as a disjunctive logic program, and \cite{lager_nivre01}, which
reconstructs four different formalisms in first-order logic.
Other works combining logic to CG include
\cite{lindberg_eineborg98ilp} and \cite{asfrent14}, both using Inductive Logic Programming to learn CG rules from a tagged corpus.
%We explore different approaches to ordering. 
%In the case of unordered rules, it resembles Finite-State Intersection Grammar \cite{koskenniemi90}.
%See also \cite{lager01transformation} for discussion of ordering of the CG rules.
